\name: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-03-21 paper/main.tex
.

We spent a significant amount of time testing different evaluation
schemes for predicting drug--target interactions. This was motivated
by our finding that a na\"ive predictor can achieve a performance only
slightly below state of the art drug--target prediction methods.

>>>>

We spent a significant amount of time testing different evaluation
schemes for predicting drug--target interactions. We designed a
na\"ive predictor and find that it can achieve a performance only
slightly below state of the art drug--target prediction methods. We
investigated this finding further and

In the presence of imbalanced
